---
name: "Dr. Sarah E"
surname: "Schwartz"
position: "Research Assistant Professor"
address: "Utah State University"
phone: (435) 797-0169
www: "SarahSchwartzStats.com"
email: "Sarah.Schwartz@usu.edu"
twitter: USU_StatStudio
github: SarBearSchwartz
linkedin: SarBearSchwartz
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```


# Appointments

```{r}
tibble::tribble(
  ~position, ~year_span, ~department, ~location, ~bullet, 
  "Assistant Research Professor",
  "2015-present",
  "Psychology Department, College of Education and Human Services",
  "Utah State University",
  "Director, The Statistical Consulting Studio",
  "Assistant Research Professor",
  "2015-present",
  "Psychology Department, College of Education and Human Services",
  "Utah State University",
  "Instructor, graduate student quantitatice methods and statistics courses",
  "Statistician",
  "2013-2015",
  "Office of Research Services, College of Education and Human Services",
  "Utah State University",
  "Acting Director, Office of Methodological and Data Sciences",
  "Statistician",
  "2013-2015",
  "Office of Research Services, College of Education and Human Services",
  "Utah State University",
  "Instructor, graduate student quantitatice methods and statistics courses",
  "Statistician and Data Manager",
  "2005-2013",
  "Center for Epidemiology",
  "Utah State University",
  "Managed databases, clean data, and prepare custom datasets",
  "Statistician and Data Manager",
  "2005-2013",
  "Center for Epidemiology",
  "Utah State University",
  "Performed statistical analyses and prepared publications, posters, presentations,
and grant submissions",
  "Statistician and Data Manager",
  "2005-2013",
  "Center for Epidemiology",
  "Utah State University",
  "Worked under three main grants and many co-investigators: University of Utah,
  BYU, Duke, John Hopkins, University of Maryland, ect.",
  "Data Manager",
  "2012",
  "Kenoi Genetics Lab",
  "Brigham Young University",
  "Managed databases and prepare custom datasets",
"Adjunct Lecturer",
"2006-2008",
"Mathematics and Statistics Department",
"Utah State University",
"Traditional, evening, and distance courses",
"High School Teacher, Math and Science",
"2000-2004",
"",
"",
"Sky View High School, Smithfield, Utah",
"High School Teacher, Math and Science",
"2000-2004",
"",
"",
"Logan River Academy, Logan, Utah"
) %>%  
  vitae::detailed_entries(
    what = position,
    when =year_span,
    with = department,
    where = location,
    why = bullet
  )
```



# Education

```{r}
tibble::tribble(
  ~degree, ~year_span, ~school, ~location, ~bullet,
  "PhD: Mathetatics, Specialization in Statistics",  
  "2013-2017", 
  "Utah State University", 
  "Logan, Utah, USA", 
  "Disertation: Exact Approaches for Bias Detection and Avoidance with Small, Sparce, or Correlated Categorical Data",
  "PhD: Mathetatics, Specialization in Statistics",  
  "2013-2017", 
  "Utah State University", 
  "Logan, Utah, USA",
  "Mentor: Dr. Chris Corcoran",
  "PhD: Mathetatics, Specialization in Statistics",  
  "2013-2017", 
  "Utah State University", 
  "Logan, Utah, USA",
  "TA: Lecturer and grader",
    "PhD: Mathetatics, Specialization in Statistics",  
  "2013-2017", 
  "Utah State University", 
  "Logan, Utah, USA",
  "RA: Simulation programmer, Cytel Software Inc.",  "PhD: Mathetatics, Specialization in Statistics",  
  "2013-2017", 
  "Utah State University", 
  "Logan, Utah, USA",
  "2015: Department Academic Excellence Award",
    "PhD: Mathetatics, Specialization in Statistics",  
  "2013-2017", 
  "Utah State University", 
  "Logan, Utah, USA",
  "2014: Department Industrious Graduate Student Award",
  
  
  "MS: Statistics",  
  "2004-2006", 
  "Utah State University", 
  "Logan, Utah, USA", 
  "Thesis: Linear Mixed Effects Modeling of Neuropsychiatric Symptoms in Patients with Dementia",
  "MS: Statistics",  
  "2004-2006", 
  "Utah State University", 
  "Logan, Utah, USA", 
  "TA: Lecturer and grader",
    "MS: Statistics",  
  "2004-2006", 
  "Utah State University", 
  "Logan, Utah, USA", 
  "RA: Statistician, Center for Epidemiology Studies",
    "MS: Statistics",  
  "2004-2006", 
  "Utah State University", 
  "Logan, Utah, USA", 
  "2005: Department Graduate Student Teacher of the Year Award",  
  
  "BS: Math and Chem Secondary Education",  
  "1998-2000", 
  "Utah State University", 
  "Logan, Utah, USA", 
  "Student Teaching: Sky View High School, Smithfield, Utah"
) %>%  
  vitae::detailed_entries(
    what = degree,
    when =year_span,
    with = school,
    where = location,
    why = bullet
  )
```

# Licenses

```{r}
tibble::tribble(
  ~title, ~year_span,  ~location, ~bullet,
  "Secondary Education Teaching License",
  "2001-2009",
  "State of Utah",
  "Endorsements: mathematics level 4 and chemistry"
) %>%  
  vitae::detailed_entries(
    what = title,
    when =year_span,
    where = location,
    why = bullet
  )
```


# Software

```{r}
tibble::tribble(
  ~title,  ~bullet,
  "R, R Studio, and R Markdown (LaTeX)",
  "Data cleaning and wrangling, statistical analysis, and reproducible reporting",
  "SAS, SPSS, MPlus, and G*Power",
  "Data cleaning and wrangling, and statistical analysis",
  "REDCap and Qualtrics",
  "Creating forms and collecting data"
) %>%  
  vitae::detailed_entries(
    what = title,
    why = bullet
  )
```

\clearpage

# Publications

## Submitted

## 2016

```{r}
# bibliography_entries("publications.bib")
```



\clearpage

# Teaching: Utah State University - Graduate Courses

\vspace{0.5cm}

**PSY 7650: Multilevel and Marginal Models for the Social Sciences**

Coverage of multilevel *(ie, mixed-effects, hierarchical linear)* and marginal
*(ie, GEE)* models for both continuous and categorical outcomes. Includes
application of these methods to many types of cross-sectional and longitudinal
research designs *(eg, experimental, case-control, cohort, cross-over, complex
sample, randomized controlled trials)*.    
    
    
* Software: `R` and `R Studio`

  + 2019 Fall *(scheduled)*
  + 2018 Fall
  + 2017 Fall
  + 2016 Fall


\vspace{0.5cm}



**PSY 6600: Statistical Foundataions *(previously: Research Design and Analysis I)* **

Research design and statistical concepts for research in education, human
services, and psychology, with emphasis on the selection and interpretation of
statistical analyses.  Focus on ANOVA based methods. Includes a combination of traditional face-to-face and diatnace site students.  *(Summer sessions condensed to 7 weeks)*  


* Software: `R` and `R Studio`
    + 2019 Summer
    + 2019 Spring
    + 2018 Summer
    + 2018 Spring

* Software: `SPSS`
   + 2017 Summer
   + 2017 Spring
   + 2016 Summer
   + 2015 Summer




\clearpage

# Teaching: Utah State University - Undergraduate Courses



\vspace{0.5cm}



**STAT 2000: Statistical Methods**

Introduction to statistical concepts, graphical techniques, probability, distributions, estimation, one and two sample testing, chi-square tests, and simple
linear regression, one-way ANOVA.    

* Software: `StatCrunch`
    + 2014 Fall
    + 2014 Spring
    + 2005 Fall
    + 2005 Spring


\vspace{0.5cm}



**STAT 1040 Introduction to Statistics**

Descriptive and inferential statistical methods. Emphasis on conceptual understanding and statistical thinking. Examples presented from many different
areas.    

* Software: *none*
    + 2008 Spring, mostly distance sites
    + 2007 Fall
    + 2007 Spring
    + 2006 Fall



\vspace{0.5cm}


**MATH 1050 College Algebra**

Functions: graphs, transformations, combinations, and inverses. Polynomial,
rational, exponential, logarithmic functions, and applications. Systems of
equations and matrices. Partial fractions.    

* Software: `graphing calculators`
    + 2004 Fall



\vspace{0.5cm}



**MATH 1010 Intermediate Algebra**    

Review of introductory algebra concepts. Topics include manipulating and
simplifying expressions, solving equations and inequalities, graphing equations, and inequalities. Real world applications including linear, quadratic, polynomial, rational, exponential, and radical functions.    

* Software: *none*
    + 2006 Summer
